Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-09 exp1/iswc2013.tex
Use normal plot with two levels
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@552 43ef1190-90fd-4dd7-a769-d0121f02b80e

We turn to the 64-run experiment and its normal plot in
figure~\ref{fig:frac64normalalpha005}. We see that the we get more significant
effects, and that they correspond well to those we saw in the full
factorial experiment. They also all have an intuitive
explanation as above. However, we do not see the effects that we found
worrisome in the full factorial design. The ``Implement:TripleC''
interaction emerges only for a level $\alpha=0.15$, see
figure~\ref{fig:frac64normalalpha015}. To ensure that we discover such
cases will be a key challenge in further studies.

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{frac64normalalpha005.pdf}
  \caption{A normal plot of the Fractional Factorial Experiment with
    64 runs. The labelled points are considered significant by using
    the Lenth criterion at a level
    $\alpha=0.05$.}\label{fig:frac64normalalpha005}
\end{figure}
\begin{figure}[hb]
  \includegraphics[width=\textwidth]{frac64normalalpha015.pdf}
  \caption{A normal plot of the Fractional Factorial Experiment with
    64 runs. The labelled points are considered significant by using
    the Lenth criterion at a level
    $\alpha=0.15$.}\label{fig:frac64normalalpha015}
\end{figure}

>>>>

We turn to the 64-run experiment and its normal plot in
figure~\ref{fig:frac64normal}. We see that the we get more significant
effects, and that they correspond well to those we saw in the full
factorial experiment. They also all have an intuitive
explanation as above. However, we do not see the effects that we found
worrisome in the full factorial design. The ``Implement:TripleC''
interaction emerges only for a level $\alpha=0.15$. To ensure that we discover such
cases will be a key challenge in further studies.

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{frac64normal.pdf}
  \caption{A normal plot of the Fractional Factorial Experiment with
    64 runs. The labelled points are considered significant by using
    the Lenth criterion. Triangles correspond to a level $\alpha=0.15$
    and crosses at $\alpha=0.05$.}\label{fig:frac64normal}
\end{figure}
